{\fontfamily{ptm}\selectfont Reading Notes}

### 2025-06-19 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, new stuff

            The following theorem stated their use of the this error bound to capture a class of Q-SCNVX function. 

@@

                    \item $f \in \mathbb S'$ which is the hypothesis that $f$ is Q-CNVX. 
                    \item $\alpha_k \le L_f^{-1}$, the stepsize is sufficient to apply descent lemma globally. 

@@

        \subsection{Monotone routines}
            % BECK'S MONO ------------------------------------------------------
            \begin{algorithm}[H]
                \begin{algorithmic}[1]
                    \STATE{\noindent
                        \textbf{Function BeckMono Inputs: }
                        \begin{tabular}{|ll}
                            $f: \RR^n \rightarrow \RR$ & Convex Smooth\\
                            $g: \RR^n \rightarrow \overline \RR$ & Convex\\
                            $\tilde x \in \RR^n$ & Vector\\
                            $x \in \RR^n$ & Vector\\
                            $\rho$ & Number $\rho \in (0, 1)$ Number\\
                            $G \in \RR$ & Number 
                        \end{tabular}\vspace{0.5em}
                    }
                    \STATE{\noindent
                        $x^+ = \argmin \{(f + g)(z): z \in \{\tilde x, x\}\}$. 
                    }
                    \STATE{\textbf{Return: } $x^+, \eta, G$}
                    \caption{Beck's monotone routine}\label{alg:beck-mono}
                \end{algorithmic}
            \end{algorithm}
            \par
            Algorithm \ref{alg:beck-mono} is a subroutine for asserting monotone condition on function value. 
            The parameter $G$ has no actual usage besides making it compatible with Algorithm \ref{alg:nes-mono} in the context of Algorithm \ref{alg:xxapg}. 
            The input $\tilde x$ is the candidate iterate produced by FISTA without monotone constraints and $x$ is the previous iterates $x_{k - 1}$ in the inner loop. 
            % NES'S MONO -------------------------------------------------------
            \begin{algorithm}[H]
                \begin{algorithmic}[1]
                    \STATE{\noindent
                        \textbf{Function NesMono Inputs: }
                        \begin{tabular}{|ll}
                            $f:\RR^n\rightarrow \RR$ & Lipschitz Smooth \\ 
                            $g: \RR^n \rightarrow \overline \RR$ & Weakly Convex \\ 
                            $\tilde x \in \RR^n$ & Vector \\ 
                            $x \in \RR^n$ & Vector \\
                            $\eta \in \RR$ & Number $\eta > 0$\\
                            $G \in \RR$  & Number
                        \end{tabular}\vspace{0.5em}
                    }
                    \STATE{\noindent
                        $\hat y := \argmin\{(f + g)(z), x \in \{\tilde x, x\}\}$. 
                    }
                    \STATE{\noindent
                        $x^+ := T_{1/\eta}(\hat y)$. 
                    }
                    \FOR {i = 1, 2, \ldots, 53}
                        \IF{$(f + g)(x^+) - (f + g)(\hat y) \le -1/(2\eta)\Vert \mathcal G_{1/\eta}(\hat y)\Vert^2$}
                            \STATE{\textbf{Break}}
                        \ENDIF
                        \STATE{$\eta := 2\eta$. }
                            \STATE{$x^+ := T_{1/\eta}(\hat y)$.}
                    \ENDFOR
                    \STATE{$G := \eta (x^+ - \hat y).$}
                    \STATE{\textbf{return: } $x^+, \eta, G$ }
                    \caption{Nesterov's monotone routine}\label{alg:nes-mono}
                \end{algorithmic}
            \end{algorithm}
            \par
            The above Algorithm \ref{alg:nes-mono} implements and adapts Nesterov's monotone scheme from Nesterov \cite[2.2.32]{nesterov_lectures_2018} for \XXAPG{}. 
            In addition to Algorithm \ref{alg:beck-mono}, $\eta$ is a new input parameter and $G$ has a significance role. 
            $\eta$ is a stepsize parameter for weakly convex objective $F = f + g$ satisfying Assumption \ref{ass:sum-of-wcnvx}. 
            $G$ is the norm of the gradient mapping updated at $\hat y$ which will be returned to the inner loop to verify exit conditions.

@@

        Both $(n_j)_{j\ge0}, (p_j)_{j\ge 0}$ are nondecreasing sequences. 

>>>>

            The following theorem stated their use of the error bound to capture a class of Q-SCNVX function. 

@@

                    \item $f \in \mathbb S'$ which is the hypothesis that $f$ is Q-SCNVX. 
                    \item $\alpha_k \le L_f^{-1}$, the step size is sufficient to apply descent lemma globally. 

@@

        \subsection{Monotone routines}
            % BECK'S MONO ------------------------------------------------------
            \begin{algorithm}[H]
                \begin{algorithmic}[1]
                    \STATE{\noindent
                        \textbf{Function BeckMono Inputs: }
                        \begin{tabular}{|ll}
                            $f: \RR^n \rightarrow \RR$ & Convex Smooth\\
                            $g: \RR^n \rightarrow \overline \RR$ & Convex\\
                            $\tilde x \in \RR^n$ & Vector\\
                            $x \in \RR^n$ & Vector\\
                            $\rho$ & Number $\rho \in (0, 1)$ Number\\
                            $G \in \RR$ & Number 
                        \end{tabular}\vspace{0.5em}
                    }
                    \STATE{\noindent
                        $x^+ = \argmin \{(f + g)(z): z \in \{\tilde x, x\}\}$. 
                    }
                    \STATE{\textbf{Return: } $x^+, \eta, G$}
                    \caption{Beck's monotone routine}\label{alg:beck-mono}
                \end{algorithmic}
            \end{algorithm}
            \par
            Algorithm \ref{alg:beck-mono} is a subroutine for asserting monotone condition on function value. 
            The parameter $G$ has no actual usage besides making it compatible with Algorithm \ref{alg:nes-mono} in the context of Algorithm \ref{alg:xxapg}. 
            The input $\tilde x$ is the candidate iterate produced by FISTA without monotone constraints and $x$ is the previous iterates $x_{k - 1}$ in the inner loop. 
            % NES'S MONO -------------------------------------------------------
            \begin{algorithm}[H]
                \begin{algorithmic}[1]
                    \STATE{\noindent
                        \textbf{Function NesMono Inputs: }
                        \begin{tabular}{|ll}
                            $f:\RR^n\rightarrow \RR$ & Lipschitz Smooth \\ 
                            $g: \RR^n \rightarrow \overline \RR$ & Weakly Convex \\ 
                            $\tilde x \in \RR^n$ & Vector \\ 
                            $x \in \RR^n$ & Vector \\
                            $\eta \in \RR$ & Number $\eta > 0$\\
                            $G \in \RR$  & Number
                        \end{tabular}\vspace{0.5em}
                    }
                    \STATE{\noindent
                        $\hat y := \argmin\{(f + g)(z), x \in \{\tilde x, x\}\}$. 
                    }
                    \STATE{\noindent
                        $x^+ := T_{1/\eta}(\hat y)$. 
                    }
                    \FOR {i = 1, 2, \ldots, 53}
                        \IF{$(f + g)(x^+) - (f + g)(\hat y) \le -1/(2\eta)\Vert \mathcal G_{1/\eta}(\hat y)\Vert^2$}
                            \STATE{\textbf{Break}}
                        \ENDIF
                        \STATE{$\eta := 2\eta$. }
                            \STATE{$x^+ := T_{1/\eta}(\hat y)$.}
                    \ENDFOR
                    \STATE{$G := \eta (x^+ - \hat y).$}
                    \STATE{\textbf{return: } $x^+, \eta, G$ }
                    \caption{Nesterov's monotone routine}\label{alg:nes-mono}
                \end{algorithmic}
            \end{algorithm}
            \par
            The above Algorithm \ref{alg:nes-mono} implements and adapts Nesterov's monotone scheme from Nesterov \cite[2.2.32]{nesterov_lectures_2018} for \XXAPG{}. 
            In addition to Algorithm \ref{alg:beck-mono}, $\eta$ is a new input parameter and $G$ has a significance role. 
            $\eta$ is a step size parameter for weakly convex objective $F = f + g$ satisfying Assumption \ref{ass:sum-of-wcnvx}. 
            $G$ is the norm of the gradient mapping updated at $\hat y$ which will be returned to the inner loop to verify exit conditions.

@@

        Both $(n_j)_{j\ge0}, (p_j)_{j\ge 0}$ are non-decreasing sequences. 
